---
title: "Stat 297 Homework 2"
author: "Eric, Sidharth, Kaiyi, Kai"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Question 1: Fizz Buzz
```{r}
for (i in 1:100) {
  if (i %% 3 == 0 & i %% 5 == 0) {print("Fizz Buzz")}
  else if (i %% 3 == 0) {print("Fizz")}
  else if (i %% 5 == 0) {print("Buzz")}
  else print(i)
}
```


### Question 2: Map
install.packages("ggmap")
install.packages('rvest')
library(maps)
library(ggmap)
library(rvest)

# Define webpage
big10 = read_html("http://www.bigten.org/library/stats/fb-confsked.html#standings")

# Get uni names
big10 %>% 
  html_nodes(".b1gfbstats:nth-child(9) td:nth-child(1) , .b1gfbstats:nth-child(6) td:nth-child(1)") %>% 
  html_text() -> uni_name
uni_name = paste(uni_name,"University")

# Find uni locations
uni_coord = data.frame(geocode(uni_name))

# Get win rate
big10 %>% 
  html_nodes("td:nth-child(7)") %>%
  html_text() -> uni_wp
uni_coord$wp = 100*as.numeric(uni_wp[1:length(uni_name)])

# Get division
uni_coord$conf = rep(c("East Division","West Division"), each = length(uni_name)/2)

library(mapproj)
map <- get_map(data = uni_coord, zoom = 4)
ggmap(map) + geom_point(data = uni_coord, 
                        aes(lon, lat, col = conf, size = wp)) + 
  scale_size(name="Big 10 Conference") + 
  xlab("Longitude") + ylab("Latitude")

```
